An open source scientific article

### 2024-03-08 src/tex/authors.tex
start author cleanup

\author[1]{Nawaf~Alampara~\orcidlink{}}

\author[1]{Adrian~Mirza~\orcidlink{}}

\author[1]{Sreekanth~Kunchapu~\orcidlink{}}

\author[]{Aswanth~Krishnan}

@@

@@

\author[5]{Tanya~Gupta}

\author[5]{Philippe~Schwaller~\orcidlink{0000-0003-3046-6576}}

\author[]{Michael Pieler~\orcidlink{0000-0001-9186-7045}}

\author[1,2, 3]{Kevin~Maik~Jablonka~\orcidlink{0000-0003-4894-4660}}
\affil[1]{Laboratory of Organic and Macromolecular Chemistry (IOMC), Friedrich Schiller University Jena, Humboldtstrasse 10, 07743 Jena, Germany}
\affil[2]{Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[3]{Helmholtz Institute for Polymers in Energy Applications (HIPOLE), Philosophenweg 7a, 07743 Jena, Germany}
\affil[]{\texttt{mail@kjablonka.com}}

>>>>

%Conceptualization
%Data curation
%Formal analysis - Application of statistical, mathematical, computational, or other formal techniques to analyse or synthesize study data.
%Funding acquisition
%Investigation - Conducting a research and investigation process, specifically performing the experiments, or data/evidence collection.
%Methodology
%Project administration
%Resources
%Software
%Supervision
%Validation
%Visualization
%Writing -- original draft
%Writing -- review & editing

\credit{Adrian~Mirza}{0,1,1,0,1,0,0,0,1,0,0,0,0,0}
\credit{Sreekanth~Kunchapu}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Tanya~Gupta}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Jakob~Meyer}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Michael Ringleb}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Maximilian Greiner}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Yannik Köster}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jan Peschel}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Amir Elahi}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Dinga Wonanke}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Juliane Eberhardt}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Christina Glaubitz}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Fabian Alexander Kreth}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Lea Klepsch}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
%ORCID ID:  0000-0002-5968-8706 Affiliation:    Institute for Technical Chemistry and Environmental Chemistry (ITUC) and Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany
\credit{Mara~Wilhemli}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Macjonathan~Oreke}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Benedict~Emoekabu}{0,1,0,0,1,0,0,0,0,0,0,0,0,0}
\credit{Michael~Pieler}{1,0,0,0,0,0,0,0,0,0,0,0,a0,0}
\credit{Aswanth~Krishnan}{0,0,0,0,0,0,0,0,1,0,0,0,0,0}
\credit{Philippe~Schwaller}{1,1,0,1,1,0,0,0,0,1,0,0,0,0}
\credit{Ulrich~S.~Schubert}{0,0,0,1,0,0,0,0,0,0,0,0,0,0}
\credit{Berend~Smit}{0,0,0,1,0,0,0,0,0,0,0,0,0,0}
\credit{Kevin Maik Jablonka}{1,1,1,1,1,1,1,1,1,1,1,1,1,1}

\author[1,*]{Nawaf~Alampara~\orcidlink{}}

\author[1,*]{Adrian~Mirza~\orcidlink{0000-0003-4033-4235}}

\author[1,*]{Sreekanth~Kunchapu~\orcidlink{0009-0003-5752-0154}}

\author[1]{Lea~Klepsch~\orcidlink{0000-0003-4978-4670}}
\author[1]{Jan~Peschel~\orcidlink{0009-0002-4787-2757}}
\author[1]{Jakob~Meyer}
\author[1]{Michael~Ringleb~\orcidlink{0000-0002-7320-8529}}
\author[1]{Maximilian~Greiner}
\author[1]{Yannik~Köster~\orcidlink{0000-0002-9125-3067}}

\author[1]{Ulrich~S.~Schubert~\orcidlink{0000-0003-4978-4670}}
\author[ituc]{Fabian~Alexander~Kreth~\orcidlink{0000-0002-5968-8706}}
\author[1]{Juliane~Eberhardt~\orcidlink{0009-0000-3991-0704}}
\author[dresden]{Dinga~Wonanke~\orcidlink{0000-0002-9066-2715}}
\author[lsmo]{Amir~Elahi}
\author[lsmo]{Berend~Smit~\orcidlink{0000-0003-4653-8562}}

\author[qpi]{Aswanth~Krishnan}

@@

\author[Occlu]{Christina~Glaubitz~\orcidlink{0000-0003-3412-0548}}

@@

\author[nccrcat,liac]{Tanya~Gupta}

\author[nccrcat,liac]{Philippe~Schwaller~\orcidlink{0000-0003-3046-6576}}

\author[open,stability]{Michael Pieler~\orcidlink{0000-0001-9186-7045}}

\author[1,2, 3]{Kevin~Maik~Jablonka~\orcidlink{0000-0003-4894-4660}}

\affil[1]{Laboratory of Organic and Macromolecular Chemistry (IOMC), Friedrich Schiller University Jena, Humboldtstrasse 10, 07743 Jena, Germany}
\affil[2]{Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[3]{Helmholtz Institute for Polymers in Energy Applications (HIPOLE), Philosophenweg 7a, 07743 Jena, Germany}

\affil[liac]{Laboratory of Artificial Chemical Intelligence (LIAC), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Lausanne, Switzerland.}
\affil[nccrcat]{National Centre of Competence in Research (NCCR) Catalysis, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Lausanne, Switzerland.}

\affil[lsmo]{Laboratory of Molecular Simulation (LSMO), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Sion, Valais, Switzerland.}
\affil[dresden]{Theoretical Chemistry, Technische Universität Dresden, Dresden 01062, Germany}
\affil[open]{OpenBioML.org}
\affil[stability]{Stability.AI}
\affil[ituc]{Institute for Technical Chemistry and Environmental Chemistry (ITUC) and Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[qpi]{Qpi volta}
\affil[occlu]{Occlutech GmbH, Jena, Germany}

\affil[]{\texttt{mail@kjablonka.com}}
\affil[*]{These authors contributed equally.}
